Twists of supersymmetric gauge theories

### 2019-09-20 paper.tex
couplings

\begin{proof}
We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{CE}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
&\quad + \d_{\mr{CE}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
&\quad + \d_{\mr{CE}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}. The remaining terms are those involving the action of supersymmetries.

@@

Next, we move on to the $6$-dimensional $\cN=(1,0)$ super Yang-Mills. 
The theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
\[
\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
\]
where $W$ is a (complex) $2$-dimensional symplectic vector space. 
The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation. 
The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I_{\rm gauge}^{(1)}(Q) & = \int \<A^*, \Gamma(Q, \lambda_+)\> + \<\lambda^*, \sd F_A Q\> \\
I_{\rm gauge}^{(2)}(Q_1 \otimes Q_2) & = \int \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>  .
\end{align*}
These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, as the following proposition states. 
Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.

\begin{prop}[\cite{SWchar}]
The functional
\[
\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I_{\rm gauge}^{(1)} + I_{\rm gauge}^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm gauge}) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS_{\rm gauge} + \frac{1}{2} \{\fS_{\rm gauge}, \fS_{\rm gauge}\} \right) = 0 .
\]
\end{prop}
\begin{proof}
\brian{Do this already! It's almost identical to the proof in 4d, just need to do a bit of translation.} 
\end{proof}

\brian{now on to couplings...}

@@

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$). 
We note that the results in the section have appeared in \cite{SW4d}.

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric Yang-Mills theory numerous times. 
The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]

Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
Super Yang-Mills couples to the matter via the action 
\[
S_{\rm couple} = \int \d^4 x \;
\]
Let $S_{\rm BV}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

@@

@@

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on. 
Such supercharges are minimal (i.e. have 2d image).  
They are stabilized by $\SU(2)$ \brian{really $U(2)$, i think} \chris{Agreed: a minimal square zero spinor of positive helicity is stabilized by $\SU(2)_-$, but also by a torus in $\SU(2)_+$.}.  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the $\SU(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto c \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda & \mapsto \chi + \psi_{1,0} + B_{0,2} \in \Omega^0(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg)
\end{align*}

@@

\begin{prop}[\cite{SWchar}]
The minimal twist of 4d $\cN=1$ super Yang-Mills coupled to the $\cN=1$ chiral multiplet on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory coupled to the holomorphic $\beta\gamma$ system. 
\end{prop}
%
%The matter sector of the theory is labeled by the BRST fields:
%\begin{itemize}
%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
%\end{itemize} 
%which together define the (abelian) local Lie algebra
%\[
%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
%\]
%\subsection{Dimension 3}

>>>>

\begin{proof}
We can filter the complex $\clie^\bu(\mf A) \otimes \cloc^\bu(\fL)$ by the number of anti-field components in $\fL$.  Using this filtration, the left-hand side of \ref{nd_MC} splits up as
\begin{align}
\d_{\rm Lie}  \left( \fS \right) + \frac{1}{2} \left\{ \fS , \fS \right\} &= \d_{\mr{CE}} I_{\mr{Poin}} + \frac 12 \{S_{\mr{BV}} + I_{\mr{Poin}}, S_{\mr{BV}} + I_{\mr{Poin}}\} \label{MC_BV}\\
&\quad + \{S_{\mr{BV}}, I^{(1)}\} \label{MC_1}\\
&\quad + \d_{\mr{CE}} I^{(1)} + \{I_{\mr{Poin}}, I^{(1)}\} + \{S_{\mr{BV}}, I^{(2)}\} + \frac 12 \{I^{(1)}, I^{(1)}\} \label{MC_2}\\
&\quad + \d_{\mr{CE}} I^{(2)} + \{I_{\mr{Poin}}, I^{(2)}\} + \{I^{(1)}, I^{(2)}\} \label{MC_3}\\
&\quad + \frac 12 \{I^{(2)}, I^{(2)}\}. \label{MC_4}
\end{align}
Taking these terms one at a time, we first note that the vanishing of the first term, \ref{MC_BV}, is just the fact that the BV action of the 10d super Yang-Mills theory \brian{here is a statement about 10d, but the theorem is about dimensions 3,4, 6, 10} satisfies the classical master equation, and is Poincar\'e invariant, as in Proposition \ref{YM_Poincare_invariant_prop}. The remaining terms are those involving the action of supersymmetries.

@@

Next, we move on to the $6$-dimensional $\cN=(1,0)$ super Yang-Mills. 
The theory has BRST fields given by a ghost $c$, a $6$-dimensional gauge field $A$, and a Lie algebra valued spinor
\[
\lambda_+ \in \Omega^0(\RR^6) \otimes S_+^{6d} \otimes W \otimes \fg 
\]
where $W$ is a (complex) $2$-dimensional symplectic vector space. 
The tensor product $S_+^{6d} \otimes W$ forms the $8$-dimensional symplectic Weyl representation. 
The action of supersymmetry on the $6$-dimensional matter theory is encoded by a linear and quadratic functional:
\begin{align*}
I_{\rm gauge}^{(1)}(Q) & = \int \<A^*, \Gamma(Q, \lambda_+)\> + \<\lambda^*, \sd F_A Q\> \\
I_{\rm gauge}^{(2)}(Q_1 \otimes Q_2) & = \int \left\<\lambda^* \;,\; \rho(\Gamma(Q_1,Q_2)) \lambda^* + \frac 12 \left((Q_2, \lambda^*)Q_1 + (Q_1, \lambda^*)Q_2\right)\right\>  .
\end{align*}
These functionals define an off-shell action of the $\cN = (0,1)$ supersymmetry on the vector multiplet, which we proved above in Theorem \label{SUSY_YM_theorem}, and state below as a proposition. 
Below, $\fL_{\rm gauge}$ denotes the local Lie algebra describing super Yang-Mills, and $S_{\rm BV, gauge}$ is the full BV action.

 implies the following proposition for $6d$
\begin{prop}[special case of Theorem \ref{SUSY_YM_theorem}]
The functional
\[
\fS_{\rm gauge} = S_{\rm BV, gauge} + I_{\rm Poin} + I_{\rm gauge}^{(1)} + I_{\rm gauge}^{(2)} \in \clie^\bu(\mf A) \otimes \cloc^\bu(\fL_{\rm gauge}) [-1]
\]
satisfies the Maurer-Cartan equation
\[
\left(\d_{\rm Lie} \fS_{\rm gauge} + \frac{1}{2} \{\fS_{\rm gauge}, \fS_{\rm gauge}\} \right) = 0 .
\]
\end{prop}

@@

The 4-dimensional $\mc N=1$ pure super Yang-Mills theory has BRST fields given by a ghost $c$, a 4d gauge field $A$, and a Lie algebra valued Weyl spinor field $\lambda$. 
In addition, $4$-dimensional supersymmetry supports a chiral (or anti-chiral) matter multiplet, which comprises a complex scalar $\phi$ and a left (right) Weyl spinor $\psi_+$ ($\psi_-$).

The most general theory $4$-dimensional $\mc N = 1$ theory we will consider is super Yang-Mills theory valued in a Lie algebra $\fg$ coupled to a chiral multiplet with values in a complex $\fg$-representation $R$. 
This means that the fields $\phi, \psi_+$ take values in $R$ and $\Bar{\phi}, \psi_-$ take values in $R^*$. 
We have written down the action for supersymmetric pure Yang-Mills theory numerous times, which we call $S_{\rm gauge}$ here. 
The kinetic part of the action functional for $4$-dimensional $\mc N = 1$ matter is of the form
\[
S_{\rm matter} (\phi, \Bar{\phi}, \psi_+, \psi_-) = \int \d^4 x \; \<\partial_{x_i} \phi , \partial_{x_i} \Bar{\phi}\>_R + \int \d^4 x \; \<\psi_+ , \sd \dd \psi_-\>_R .
\]

Here $\<-,-\>_R$ incorporates the obvious pairing between $R$ and $R^*$. 
There is also a term $S_{\rm couple}$ describing the coupling between Yang-Mills and the matter fields. 
Since we will not need the explicit form of the coupling in the untwisted theory, we do not give the formula here. 
Let $S_{\rm BV} = S_{\rm gauge} + S_{\rm matter} + S_{\rm couple}$ denote the full BV action of $\mc N = 1$ super Yang-Mills coupled to matter.

@@

These functionals prescribe an off-shell action of $4$-dimensional $\cN=1$ super Yang-Mills coupled to matter, as we state in the following proposition.
The result appears in \cite{SWchar}, and we do not repeat the proof here.

@@

There is a single non-zero equivalence class of square zero supercharges in $4$-dimensional $\mc N = 1$, which we fix from here on. 
Such supercharges are minimal (i.e. have 2d image).  
They are stabilized by ${\rm U}(2)$; indeed a minimal square zero spinor of positive (negative) helicity is stabilized by $\SU(2)_-$ ($\SU(2)_+$), but also by a torus in $\SU(2)_+$ ($\SU(2)_-$).  
The R-symmetry group is $U(1)$, and the twisted theory by such a supercharge can always be made $\ZZ$-graded.

We first decompose the fields of the 4-dimensional $\mc N=1$ theory with respect to the ${\rm U}(2)$ stabilizer.
The fields of the pure Yang-Mills part decomposes as:
\begin{align*}
c & \mapsto c \in \Omega^0(\CC^2 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \\
\lambda & \mapsto \chi + \psi_{1,0} + B_{0,2} \in \Omega^0(\CC^2 ; \fg) \oplus \Omega^{1,0}(\CC^2 ; \fg) \oplus \Omega^{0,2}(\CC^2 ; \fg)
\end{align*}

@@

There are symmetries in the untwisted theory that will remain symmetries upon twisting. 
\begin{itemize}
\item The twisted theory is a shifted cotangent theory in the BV formalism. 
This means that the action functional of the holomorphic theory must be linear in the fields $B$ and $\beta$ of the holomorphic BF and holomorphic $\beta\gamma$ system, respectively. 
\item The action functional is invariant with respect to the group $\U(2)$ symmetry, which is the stabilizer of the fixed holomorphic supercharge.
\item The action functional is translation invariant, this follows from the fact that the untwisted theory has an 
\end{itemize}

Let $\fg$ and $R$ be a Lie algebra together with a representation.
Define the following graded Lie algebra
\[
\sG_{\cN=1} = \fg[z_1,z_2] \ltimes \left(\d^2 z \; \fg^* [z_1,z_2] [-1] \oplus R[z_1,z_2][-1] \oplus \d^2 z \; R^*[z_1,z_2]\right) .
\]
Also, denote by $\CC^2_{\rm trans}$ the abelian Lie algebra which acts on $\sG_{\cN=1}$ by the constant coefficient holomorphic vector fields $\partial_1 = \frac{\partial}{\partial z_1}$ and $\partial_2 = \frac{\partial}{\partial z_2}$.

\begin{prop}
The equivalence classes of translation invariant couplings between holomorphic BF theory with values in $\fg$ and the holomorphic $\beta\gamma$ system with values in $R$ on the complex manifold $\CC^2$ are in bijective correspondence with the Lie algebra homology / cohomology:
\[
\clieu_\bu\left(\CC^2_{\rm trans}, \clie^\bu(\sG_{\cN=1})\right) [2] .
\]
\end{prop}

\begin{prop}[\cite{SWchar}]
The minimal twist of 4d $\cN=1$ super Yang-Mills with Lie algebra $\fg$ coupled to the $\cN=1$ chiral multiplet valued in a representation $R$ on \brian{a complex surface or $\CC^2$} is equivalent to holomorphic $BF$ theory for the Lie algebra $\fg$ coupled to the holomorphic $\beta\gamma$ system with values in the representation $R$. 
\end{prop}
%
%The matter sector of the theory is labeled by the BRST fields:
%\begin{itemize}
%\item Two scalars $\varphi_{\pm} \in C^\infty (\RR^4) \otimes R$;
%\item Weyl fermions $\psi_{\pm} \in \Pi C^\infty(\RR^4) \otimes S_{\pm} \otimes R$ 
%\end{itemize} 
%which together define the (abelian) local Lie algebra
%\[
%\mathcal E_{\rm matter}^{\cN=1} = C^\infty (\RR^4) \otimes R^{\oplus 2} \oplus  \Pi C^\infty(\RR^4) \otimes (S_{+}  \otimes R \oplus S_- \otimes R) .
%\]
%\subsection{Dimension 3}
